|

### 2020-11-30 manuscript/article.Rmd
commit 1 11/29

>>>>

```{r, echo = FALSE, results='hide', warning=FALSE, message=FALSE}
fulldat$usemeta2 <- factor(fulldat$usemeta)
levels(fulldat$usemeta2) <- c("Other Coefficients", "Main Coefficients")
fulldat$usemeta2 <- as.character(fulldat$usemeta2)
fulldat$usemeta2 <- factor(fulldat$usemeta2)
aux <- select(fulldat, usemeta2, indepvar2, year, published,
              elecsys2, method) %>%
  rename(`Independent Variables` = indepvar2,
         `Year` = year,
         `Published work` = published,
         `Electoral system` = elecsys2,
         `Estimation method` = method)

res <- export2latex(
  descrTable(~.-usemeta2, aux, y = aux$usemeta2,
             show.p.overall = F, show.all = T, all.last = T), 
  caption = 'Descriptive Statistics of Moderators\\label{tab:descriptive}'
)
res <- gsub(pattern = '\\[ALL\\]', 'All Coefficients', res$desc, useBytes = T)
cat(res)
```

\begin{longtable}{lccc}\caption{Descriptive Statistics of Moderators\label{tab:descriptive}}\\
\hline  
& Main Coefficients & Other Coefficients &    All Coefficients   \\ 
&       N=42        &       N=100        &    N=142    \\
\hline
\hline     
\endfirsthead 
\multicolumn{4}{l}{\tablename\ \thetable{} \textit{-- continued from previous page}}\\ 
\hline
& Main Coefficients & Other Coefficients &    All Coefficients   \\ 
&       N=42        &       N=100        &    N=142    \\ 
\hline
\hline  
\endhead   
\hline
\multicolumn{4}{l}{\textit{continued on next page}} \\ 
\endfoot   
\multicolumn{4}{l}{}  \\ 
\endlastfoot 
Independent Variables: &                   &                    &            \\ 
$\qquad$K &    12 (28.6\%)     &     33 (33.0\%)     & 45 (31.7\%) \\ 
$\qquad$N &    24 (57.1\%)     &     55 (55.0\%)     & 79 (55.6\%) \\ 
$\qquad$logN &     6 (14.3\%)     &     12 (12.0\%)     & 18 (12.7\%) \\ 
Year &    2009 (6.56)    &    2008 (5.82)     & 2008 (6.04)\\ 
Published work: &                   &                    &            \\ 
$\qquad$Yes &    36 (85.7\%)     &     93 (93.0\%)     & 129 (90.8\%)\\ 
$\qquad$No &     6 (14.3\%)     &     7 (7.00\%)      & 13 (9.15\%) \\ 
Electoral system: &                   &                    &            \\ 
$\qquad$Majoritarian &    22 (52.4\%)     &     46 (46.0\%)     & 68 (47.9\%) \\ 
$\qquad$Non-Majoritarian &    20 (47.6\%)     &     54 (54.0\%)     & 74 (52.1\%) \\ 
Estimation method: &                   &                    &            \\ 
$\qquad$OLS &    11 (26.2\%)     &     36 (36.0\%)     & 47 (33.1\%) \\ 
$\qquad$PANEL &    23 (54.8\%)     &     51 (51.0\%)     & 74 (52.1\%) \\ 
$\qquad$IV &     5 (11.9\%)     &     7 (7.00\%)      & 12 (8.45\%) \\ 
$\qquad$RDD &     3 (7.14\%)     &     6 (6.00\%)      &  9 (6.34\%)  \\

\hline
\end{longtable}
